Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-06-01 EMNLP-demo-paper/system.tex
update link

\section{Visualization System}
As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provides a window to peek into the model decision making process. 
However, the static attention alone likely does not tell the whole story. 
The proposed system utilizes a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes in others.
%
The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task. In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video).
%such as a prediction summary statistics the entire development set, as well as a scheme to update the model based

>>>>

\section{Visualization System}
As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP model follows a similar encoder, attention, and classifier structure, in which the attention stage provides a window to peek into the model decision making process. 
However, the static attention alone likely does not tell the whole story. 
The proposed system utilizes a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes in others.
%
The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task. In the following section, we will cover some of the essential components (the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=dcpTyWfBhp0}{link}).
%such as a prediction summary statistics the entire development set, as well as a scheme to update the model based
